---
title: "big function"
author: "Pascal van Luit"
date: "2 February 2020"
output: html_document
---

Other packages that are used:

```{r}
library(tidyverse)
library(lavaan)

set.seed(88)
```

Model to be used for testing:
```{r}
model <- " visual =~ x1 + x2 + x3
           textual =~ x4 + x5 + x6 "
```


Function to perform Model Modifications according to MI > x (Default being 10).
```{r}
mi_10 <- function(baseline.model, mi = 10, data){
  
  # Fitting the baseline model to the data:
  fit <- lavaan::cfa(baseline.model, data)
  
  # Obtaining the modification indices
  MIs <- lavaan::modindices(fit)
  
  # Obtaining relevant MI info:
  MIs <- MIs %>%
    arrange(-mi) %>% 
    select(lhs, op, rhs, mi)
  
  # Obtaining the first modification to be added to the model:
  mod1 <- paste(MIs[1, 1], MIs[1, 2], MIs[1, 3], sep = " ")
  
  # Adding the modification to the model:
  mod.model <- paste(baseline.model, mod1, sep = "
                     ")
  
  # # Adding modifications using a loop:
  # for (i in 1:mods) {
  #   
  # # Saving modifications that need to be made (based on MI values):
  # mod[i] <- paste(MIs[1, i], sep = " ")
  # 
  # # Adding modification to the model:
  # 
  # 
  # }
  
  # Checking output
  return(MIs)
  
}
```

Above function with for loop:
```{r}
mi_10_forloop <- function(baseline.model, mi = 10, data){
  
  # Fitting the baseline model:
  fit1 <- lavaan::cfa(baseline.model, data)
  
  # For loop for adding modifications
  for (i in 1:mods) {
    MIs[i] <- lavaan::modindices(fit[i])
    
  }
}
```

mi_10 function with while loop:
```{r}
mi_10_whileloop <- function(baseline.model, mi = 10, data){
  
  # Saving baseline model as model:
  model <- baseline.model
  
  # Fitting the model to the data:
  fit <- lavaan::cfa(model, data)
  
  # Obtaing MI values:
  MIs <- lavaan::modindices(fit)
  
    # Wrangling the MIs:
    MIs <- MIs %>%
      arrange(-mi) %>% 
      select(lhs, op, rhs, mi)
    
    # Extracting the restricted parameter with the largest MI value:
    largest.mi <- MIs[1, ]
    
    mod <- paste(largest.mi[1, 1], largest.mi[1, 2], largest.mi[1, 3], sep = " ")
  
  while(largest.mi[1, 4] > 10) {

    # Fitting model to the data
    fit <- lavaan::cfa(model, data)

    # Obtaining MI values:
    MIs <- lavaan::modindices(fit)

      # Wrangling the MIs:
      MIs <- MIs %>%
        arrange(-mi) %>%
        select(lhs, op, rhs, mi)

      # Extracting the modification to be added to the model:
      mod <- paste(MIs[1, 1], MIs[1, 2], MIs[1, 3], sep = " ")

      # Adding the modification to the model:
      model <- paste(model, mod, sep = "
                     ")
      print(model)
  }
    
  # return(MIs)
}
```


Testing mi_10 function:
```{r}
mi_10_whileloop(baseline.model = model, data = HolzingerSwineford1939)
```






Arguments;
- baseline.model: the base line which is defined in lavaan syntax.
- min.mi: minimum modification index value for considering a model modification.
- data: dataset on which the model is fit.
- split: percentage of observations placed in the training set.

```{r}
mi_cv <- function(baseline.model, min.mi, data, split){
  # Adding a column to the dataset to allow a train-validation split:
  data <- data %>% 
           mutate(split = rep(c("train", "test"),
                               times = c(round(split * nrow(data)), round((1 - split) * nrow(data)))))
  
  # Making a separate training set:
  train <- data %>%
            filter(split == "train") %>% 
            select(-split)
  
  test <- data %>%
            filter(split == "test") %>% 
            select(-split)
  
  # Fitting the baseline model to the training set:
  fit.train <- lavaan::cfa(baseline.model, train)
  
    # Fitting the baseline model to the test set to obtain a baseline estimate of chi-square model fit:
    fit.test <- lavaan::cfa(baseline.model, test)
    
      #A matrix to store the baseline values of model fit in test set:
      test.baseline.mat <- matrix()
    
      # Obtaining the chi-square value, p-value and degrees of freedom:
      fit.measures.test         <- fitmeasures(fit.test)
      test.baseline.mat$chisq   <- fit.measures.test["chisq"]
      test.baseline.mat$pvalue  <- fit.measures.test["pvalue"]
      test.baseline.mat$df      <- fit.measures.test["df"]
  
  # Obtaining the MIs:
  mi.train <- lavaan::modindices(fit.train)
  
    # Ordering the MIs from largest to smallest:
    mi.train <- mi.train[order(-mi.train$mi), ]
    
    # Taking only the relevant columns:
    mi.train <- mi.train[, 1:4]
    
      # Extracting the first row from those relevant columns:
      lhs <- mi.train[1, 1]
      op  <- mi.train[1, 2]
      rhs <- mi.train[1, 3]
      
      # The first modification to be added to the model:
      mod1 <- paste(lhs, op, rhs, sep = " ")
      
    # Adding the first modification to the model:
      ############################
      # No idea how to do this yet..........................
      # Need to find out a way to add a line of text to the text object
      # USE PASTE
      ############################
      new.model <- paste(baseline.model, mod1, sep = "
                         ")
    
    
    # After adding a modification to the model, the model fit on the test set must be obtained and compared to the previous model fit on the test set. This, to check if there is an improvement
    fit.test.mod <- lavaan::cfa(new.model, test)  
    sum.fit.test.mod <- summary(fit.test.mod)
    
    # Checking the model diagram with the modification:
    # diagram <- semPaths(fit.test.mod, title = FALSE, curvepivot = TRUE)
      
      
        
    # return for checking:
    #return(test.baseline.mat)
    return(diagram)
}
  
```


Testing out function mi_cv:
```{r}
model <- " visual =~ x1 + x2 + x3
           textual =~ x4 + x5 + x6 "

test <- mi_cv(baseline.model = model, data = HolzingerSwineford1939, split = 0.7)

test

```



Things to add:
  - folds
